Topological Eulerian Synthesis of Slow Motion Periodic Videos

### 2018-02-04 Paper/paper.tex
small tweak

\textbf{Preprocessing.} The input to our method is a 3-channel video of $N$ frames, each frame of resolution $W \times H$. We treat each frame as a point in Euclidean space of dimension $\mathbb{R}^{3 \cdot W \cdot H}$, and denote the set of all videos by the sequence $\mathbf{X}(t) \in \mathbb{R}^{(3 \cdot W \cdot H)}$ for integer-valued $t \in [1,N]$. The steps of our approach outlined in Figure~\ref{fig:ConceptFigure}(a-c), however, do not rely on the {\em extrinsic} geometry of the set of points $\mathbf{X}(t)$, only its set of {\em pairwise distances}. Thus, we can project all of the points into a lower-dimensional space and apply the set of techniques to the projection, assuming that the projection preserves pairwise distances. Since $N \ll (3 \cdot W \cdot H)$, we can easily project all frames into a $N-1$-dimensional space such that all distances are preserved. Denoting this projection by $\mathbf{P} \in \mathbb{R}^{(3 \cdot W \cdot H) \times (N-1)}$, our method for steps (a)-(c) operates on $\mathbf{Z}(t) = \mathbf{P} \mathbf{X}(t)$.

>>>>

\textbf{Preprocessing.} The input to our method is a 3-channel video of $N$ frames, each frame of resolution $W \times H$. We treat each frame as a point in Euclidean space of dimension $\mathbb{R}^{3 \cdot W \cdot H}$, and denote the set of all videos by the sequence $\mathbf{X}(t) \in \mathbb{R}^{(3 \cdot W \cdot H)}$ for integer-valued $t \in [1,N]$. The steps of our approach outlined in Figure~\ref{fig:ConceptFigure}(a-c), however, do not rely on the {\em extrinsic} geometry of the set of points $\mathbf{X}(t)$, only its set of {\em pairwise distances}. Thus, we can project all of the points into a lower-dimensional space and apply the set of techniques to the projection, assuming that pairwise distances are preserved. Since $N \ll (3 \cdot W \cdot H)$, the frames can be projected into a $N-1$-dimensional space such that all distances are preserved. Denoting this projection by $\mathbf{P} \in \mathbb{R}^{(3 \cdot W \cdot H) \times (N-1)}$, our method for steps (a)-(c) operates on $\mathbf{Z}(t) = \mathbf{P} \mathbf{X}(t)$.
